Relational Parametricity for Algebraically Indexed Types

### 2012-06-12 paper/section-background.tex
Add AUCTeX commands to deal with multifile document
Some notes on background work
Major changes
- Refined set of contributions
- "Complete" the motivating examples section
- Fill in some references for the background section
- "Complete" the general framework section
- Sketch the "consequences" section
- Sketch the "discussion" section

>>>>

\begin{enumerate}
\item Reynolds \cite{reynolds83types}
\item Kennedy \cite{kennedy97relational}
\item Gallier (for information on geometry) \cite{gallier11geometric}
\item Tse and Zdancewic, and Sabelfeld and Sands, for information flow \cite{sabelfeld01per}
\item Chaudhuri, Gulwani and Lublinerman, for continuity analysis \cite{chaudhuri10continuity}
\end{enumerate}

We discuss further related work in \autoref{sec:discussion}.

%%% Local Variables:
%%% TeX-master: "paper"
%%% End:
